Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-09 paper.tex
Fix deleted content.
Done.

% Document-specific definitions
\newcommand{\beq}{\begin{eqnarray

@@

\begin{abstract}
TODO
\end{abstract}

@@

Wikipedia successful decentralized.

Efficiency Performance

Coeditor network

NK Simulations

@@

\begin{table*}

@@

@@

\begin{figure*}
\includegraphics[width=6.67in,height=1.33in]{fig-deg-eff.pdf}
\includegraphics[width=6.67in,height=1.33in]{fig-deg-perf.pdf}
\caption{
TODO
\label{fig:deg-eff-perf}
}
\end{figure*}

@@

TODO

>>>>

% Document-specific definitions
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\+}{\phantom{-}}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA} 
%\acmYear{1997}
%\copyrightyear{2016}

%\acmPrice{15.00}

\begin{document}
\title{Network Structure, Efficiency, and Performance in WikiProjects}

% ACM
%\author{Edward L. Platt}
%\affiliation{%
%  \institution{University of Michigan}
%  \city{Ann Arbor} 
%  \state{Michigan} 
%}
%\email{elplatt@umich.edu}

% Manuscript
\author{Edward L. Platt \\ University of Michigan \\ Ann Arbor, Michigan \\ elplatt@umich.edu}

% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}

% ACM
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%\end{CCSXML}

@@

\begin{abstract}
The internet has enabled collaborations at a scale never before possible,
but the best practices for organizting such large collaboartions are still not clear.
Wikipedia is a visible and successful example of such a collaboration which might offer
insight into what makes large-scale, decentralized collaborations successful.
We analyze the relationship between the structural properties of WikiProject coeditor networks
and the performance and efficiency of those networks.
We also perform numerical simulations to determine whether social learning on an NK model can
reproduce the behavior observed on Wikipedia.
We find several results seen in numerical and small-scale lab studies:
a tradeoff between performance and efficiency and
higher performance with less skewed node distributions and shorter path lengths.
We also see behaviors not previously identified: an association between low degree coeditor networks
and both higher performance and higher efficiency,
suggesting possible benefits to decentralized collaborations made of smaller, more tightly-knit teams.
We also propose a novel consensus-based social learning strategy that is both more efficient and higher
performance than existing strategies, and reproduces some behaviors seen in WikiProjects.
\end{abstract}

@@

The internet has enabled collaborations at a scale never before possible, a global scale.
Wikipedia is one of the most successful and visible of these collaborations,
and is particularly interesting for its highly decentralized structure with very little top-down control.
It is notoriously difficult to organize even small groups without top-down control,
and yet Wikipedia, with millions of editors, somehow functions.
A better theoretical understanding of projects like Wikipedia is highly desireable as it could
help inform the design of new collaborative projects.
We focus on one aspect of organizing a large-scale decentralized collaboration: the network structure.
If Wikipedia is not structured as a top-down hierarchy, how is it structured?
And how does that structure influence its success?

We approach these questions by analyzing WikiProjects on the English-language Wikipedia.
WikiProjects are collections of thematically related articles,
each with their own standards, norms, and processes for evaluating and improving articles.
We analyze the coeditor networks of these projects: which editors have worked together on at least
one article?
In particular, we examine the relationship between the structure of a project's coeditor network
and the performance and efficiency of its articles.
Performance represents the ability of a project to get articles to a high quality level,
while efficiency represents the ability to improve articles of any level quickly.
We also perform numerical simulations to compare the behavior observed on Wikipedia to the results
of several variants of a simple networked social learning model.

@@

\begin{table*}[!ht]

@@

\begin{figure*}
\includegraphics[width=6.67in,height=1.33in]{fig-deg-eff.pdf}
\includegraphics[width=6.67in,height=1.33in]{fig-deg-perf.pdf}
\caption{
Efficiency and Performance of social learning strategies vs network degree.
Each point represents a single trial of 300 iterations.
The consensus strategy shows increased performance and decreased efficiency as
degree increases, while other strategies show no degree dependence.
\label{fig:deg-eff-perf}
}
\end{figure*}

@@

@@

In this paper, we have described the relationship between the structural properties of WikiProject
coeditor networks and the performance and efficiency of those networks.
As in other studies, we see a tradeoff between performance and efficiency,
but not an absolute tradeoff.
Some properties, such as low degree, are associated with both higher performance and higher efficiency.
We also find that the correlations between path length and performance are consistent with a conformity-based
social learning strategy, but not a greedy best-neighbor strategy.
We also observe improved performance in more decentralized project, as has been seen in small-scale lab experiments.
While the performance and efficiency of most previously-studied social learning strategies depend more on path lenght than
degree,
we have proposed a novel consensus learning strategy that is more realistic, more efficient, and higher performance than
existing strategies.
While the efficiency and performance of existing strategies do not exhibit any degree-dependence, our consensus strategy
demonstrates that degree-dependence is possible.
While additional work is needed to determine causal relationships and how generalizable our results are,
we have shown evidence that several phenomena predicted by numerical and small-scale lab experiments are present in a large,
real-world network.
And, we have identified new behaviors not explained by existing models, suggesting the need for alternate models.
Our results suggest that the success of large-scale collaborations may be aided by greater decentralization,
consensus or conformity-baased decision-making, and more tightly-knit collaborations between smaller teams.
